---
name: David 
surname: Dobrowski
qualifications: BCom(Hons), BSc
position: "Director of Data, Research and Partnerships"
address: "Salinas, CA"
phone: +1 831 886 7177
www: daviddobrowski.com
email: "david@daviddobrowski.com"
twitter: dobrowski
github: dobrowski
linkedin: dobrowski
headcolor: 414141
date: "`r format(Sys.time(), '%B %Y')`"
output: 
  vitae::awesomecv:
    keep_tex: true
knit: (function(inputFile, encoding) { 
    rmarkdown::render( 
      input       = inputFile, 
      encoding    = encoding, 
      output_file = "Dobrowski Resume") })


---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(tidyverse)
library(readxl)
library(lubridate)
library(glue)
library(fontawesome) # https://github.com/loreabad6/R-CV/blob/master/CV.Rmd
library(emojifont)
# output types  AwesomeCV  moderncv  




jobs <-
  read_xlsx(here::here("data", "resume.xlsx"), sheet = "jobs") %>%
  # fill(Start, End, What, With, Where, Tag) %>%
  mutate(Start = ymd(start_date),
         End = ymd(end_date)) %>%
  mutate(
    years = case_when(
      is.na(End) ~ glue("{year(Start)}--Present") %>% as.character(),
      year(Start) == year(End) ~ year(End) %>% as.character(),
      TRUE ~ glue("{year(Start)}--{year(End)}") %>% as.character()
    )
  ) %>%  # Put additional details in with different number of details per job
  mutate(escript = pmap(list(desc1, desc2, desc3, desc4, desc5, desc6, desc7, desc8, desc9, desc10, desc11, desc12, desc13, desc14), c) ,
         escript2 = purrr::map(escript, ~purrr::discard(.x, .p = is.na)))


consulting <- read_xlsx(here::here("data", "resume.xlsx"), sheet = "consulting")


conference <- read_xlsx(here::here("data", "resume.xlsx"), sheet = "conference")



honors <- read_xlsx(here::here("data", "resume.xlsx"), sheet = "honors")


 education <-   read_xlsx(here::here("data", "resume.xlsx"), sheet = "education") # %>%

#   fill(Start, End, What, With, Where, Tag) %>%  
#   mutate(Start = mdy(Start),
#          End = mdy(End)) %>% 
#   mutate(When = case_when(
#     is.na(End) ~ glue("{year(Start)}--Present") %>% as.character(),
#     year(Start) == year(End) ~ year(End) %>% as.character(),
#     TRUE ~ glue("{year(Start)}--{year(End)}") %>% as.character()
#   ))




```
I have been consistently recognized as a valuable collaborator through the development and use of data, evaluation and learning. My work bridges the technical with the application in public service and community based organizations. I translate complex data in to forms and ideas that people can understand and use to take action.

# Skills

\begin{minipage}[t]{0.5\textwidth}
 * Advanced use of R \\
 * Evaluation \\
 * Group facilitation and training \\
\end{minipage}
\begin{minipage}[t]{0.5\textwidth}
 * Project Management \\
 * Spanish \\
\end{minipage}


# Relevant Employment


\footnotesize



```{r jobs}

jobs  %>%
  arrange(desc(start_date)) %>%
  detailed_entries(
    what = position,
    when = years,
    with = organization,
    where = location,
    why = escript2
    )

```

# Independent Consulting


\footnotesize
I have maintained my own independent evaluation consulting practice since 2007.  My clients are non-profits, foundations and government entities. 

```{r consulting}

consulting %>%
  brief_entries(
what = Clients
  )
```


# Education


```{r}
library(tibble)


education %>%
  arrange(desc(date)) %>%
  detailed_entries(
    what = degree,
    when = date,
    where = school,
    with = glue("{city}, {state}"),
    why = details
  )

```


# Select Conference Presentations
\footnotesize

```{r conference}

conference %>%
  brief_entries(
what = title,
with = place,
when = date
  )
```



# Honors and Awards 
\footnotesize
The following are select honors and awards I have received over my career.  

```{r honors}

honors %>%
  brief_entries(
what = honors,
with = place,
when = date
  )
```





```{r}
# scholar::get_publications("EmD_lTEAAAAJ&EmD_lTEAAAAJ&") %>% 
#   filter(cites > 30) %>% 
#   distinct(title, .keep_all = TRUE) %>%
#   transmute(bibtype = "Article", author = as.character(author),
#             title = as.character(title),
#             journaltitle = as.character(journal), year, key = row_number()) %>% 
#   RefManageR::as.BibEntry() %>% 
#   RefManageR::WriteBib("curie.bib")
# 
# bibliography_entries("curie.bib")
```

