---
name: David 
surname: Dobrowski
qualifications: BCom(Hons), BSc
position: "Director of Data, Research and Partnerships"
address: "Salinas, CA"
phone: +1 831 886 7177
www: daviddobrowski.com
email: "david@daviddobrowski.com"
twitter: dobrowski
github: dobrowski
linkedin: dobrowski
headcolor: 414141
date: "`r format(Sys.time(), '%B %Y')`"
output: 
  vitae::awesomecv:
    keep_tex: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(tidyverse)
library(readxl)
library(lubridate)
library(glue)
# output types  AwesomeCV  moderncv  



jobs <-
  read_xlsx(here::here("data", "resume.xlsx"), sheet = "jobs") %>%
  # fill(Start, End, What, With, Where, Tag) %>%
  mutate(Start = ymd(start_date),
         End = ymd(end_date)) %>%
  mutate(
    years = case_when(
      is.na(End) ~ glue("{year(Start)}--Present") %>% as.character(),
      year(Start) == year(End) ~ year(End) %>% as.character(),
      TRUE ~ glue("{year(Start)}--{year(End)}") %>% as.character()
    )
  )




 education <-   read_xlsx(here::here("data", "resume.xlsx"), sheet = "education") # %>%

#   fill(Start, End, What, With, Where, Tag) %>%  
#   mutate(Start = mdy(Start),
#          End = mdy(End)) %>% 
#   mutate(When = case_when(
#     is.na(End) ~ glue("{year(Start)}--Present") %>% as.character(),
#     year(Start) == year(End) ~ year(End) %>% as.character(),
#     TRUE ~ glue("{year(Start)}--{year(End)}") %>% as.character()
#   ))




```

# Some stuff about me

 * I poisoned myself doing research.
 * I was the first woman to win a Nobel prize
 * I was the first person and only woman to win a Nobel prize in two different sciences.


# Employment


\footnotesize{
My teaching quality at Monash University has been consistently recognised with positive student evaluations and individual praise from my students. I have also been awarded four congratulatory letters for outstanding student evaluations for three of my units (ETF5231, ETC3580, ETC3550), which indicates that student feedback for the unit is among the best in the university.
}

```{r jobs}
# tribble(
#   ~Year, ~Type, ~Desc,
#   1903, "Physics", "Awarded for her work on radioactivity with Pierre Curie and Henri Becquerel",
#   1911, "Chemistry", "Awarded for the discovery of radium and polonium"
# ) %>% 
#   detailed_entries(
#     glue::glue("Nobel Prize in {Type}"),
#     Year, 
#     Desc
#   )

jobs %>% 
  nest(escript = starts_with("desc"))%>%
  arrange(desc(start_date)) %>%
  detailed_entries(
    what = position,
    when = years,
    with = organization,
    where = location,
#    why = escript
    )




# jobs %>%
#    unite("descrip", desc1:desc14, na.rm = TRUE, sep = "\n") %>%
#   arrange(desc(start_date)) %>%
#   detailed_entries(
#     what = position,
#     when = years,
#     with = organization,
#     where = location,
#     why = 
#   )



# %>% 
#  detailed_entries(role, dates, company, loc, details)   # "Intern, Pricing and Promotion Analytics", "Kellogg's", "Battle Creek, MI", "May 2011 - Mar 2012", "Contributed to Kellogg's marketing and sales strategies, including optimal feature price, display partners and expected promotion lift."

```

# Independent Consulting


\footnotesize{
My teaching quality at Monash University has been consistently recognised with positive student evaluations and individual praise from my students. I have also been awarded four congratulatory letters for outstanding student evaluations for three of my units (ETF5231, ETC3580, ETC3550), which indicates that student feedback for the unit is among the best in the university.
}

```{r}
tribble(
  ~Year, ~Type, ~Desc,
  1903, "Physics", "Awarded for her work on radioactivity with Pierre Curie and Henri Becquerel",
  1911, "Chemistry", "Awarded for the discovery of radium and polonium"
) %>% 
  brief_entries(
    glue::glue("Nobel Prize in {Type}"),
    Year, 
    Desc
  )
```


# Education

```{r}
library(tibble)


# tribble(
#   ~ Degree, ~ Year, ~ Institution, ~ Where,
#   "Informal studies", "1889-91", "Flying University", "Warsaw, Poland",
#   "Master of Physics", "1893", "Sorbonne Université", "Paris, France",
#   "Master of Mathematics", "1894", "Sorbonne Université", "Paris, France"
# ) %>% 
#   detailed_entries(Degree, Year, Institution, Where)

education %>%
  arrange(desc(date)) %>%
  detailed_entries(
    what = degree,
    when = date,
    where = school,
    with = glue("{city}, {state}"),
    why = details
  )

```



# Publications

```{r}
# scholar::get_publications("EmD_lTEAAAAJ&EmD_lTEAAAAJ&") %>% 
#   filter(cites > 30) %>% 
#   distinct(title, .keep_all = TRUE) %>%
#   transmute(bibtype = "Article", author = as.character(author),
#             title = as.character(title),
#             journaltitle = as.character(journal), year, key = row_number()) %>% 
#   RefManageR::as.BibEntry() %>% 
#   RefManageR::WriteBib("curie.bib")
# 
# bibliography_entries("curie.bib")
```

